Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-10-12 methods_paper/fabl-paper.tex
formatting appendix

To aid the reader, we provide summary of the \texttt{fabl} method through pseudocode:

\begin{algorithm}[h!]
	\caption{Summary of fabl algorithm}
	\begin{algorithmic}[1]

@@

In this section, we replicate a simulation study from \cite{sadinle_bayesian_2017} to compare \texttt{fabl} against \texttt{BRL} on several simulated datasets with varying amounts of error and overlap. We use first name, last name, age, and occupation for this linkage, and create comparison vectors according to the default settings of the \texttt{compareRecords} function from the \texttt{BRL} package. See Table~\ref{Tab:sadinle_simulation_cutoffs} for details on the construction of comparison vectors. Each simulation identifies duplicated individuals between two datasets, each with 500 records. We conduct linkage when matching records exhibit 1, 2, and 3 errors across the four fields, and when there are 50, 250, and 450 individuals in common across datasets. We use flat priors for all $m$ and $u$ parameters, run the Gibbs Sampler for 1000 iterations, and discard the first 100 as burn-in.

@@

Therefore we re-ran our analysis with fewer agreement levels for each field according to Table~\ref{Tab:el_salvador_cutoffs_2}, and
obtained analogous results. With 216 possible agreement patterns, 159
were realized in the data, and our proposed method, \texttt{fabl} became much faster,
finishing in 61 seconds. Meanwhile \texttt{BRL} took 239 seconds,
relatively unchanged from the first implementation. This demonstrates
the way that the computational complexity of our method depends on the
number of unique agreement patterns, and how significant computational
gains can be made by simplifying the construction of the comparison
vectors. The estimates of the \(\mathbf{m}\) parameters under each method are very similar, as shown in
Figure~\ref{fig:m-and-u}.

@@

@@

>>>>

To aid the reader, we provide summary of the \texttt{fabl} method through pseudocode in Appendix \ref{app:fabl-psuedocode}.

@@

In this section, we replicate a simulation study from \cite{sadinle_bayesian_2017} to compare \texttt{fabl} against \texttt{BRL} on several simulated datasets with varying amounts of error and overlap. We use first name, last name, age, and occupation for this linkage, and create comparison vectors according to the default settings of the \texttt{compareRecords} function from the \texttt{BRL} package. See Table~\ref{Tab:sadinle_simulation_cutoffs} for details on the construction of comparison vectors. Each simulation identifies duplicated individuals between two datasets, each with 500 records. We conduct linkage when matching records exhibit 1, 2, and 3 errors across the four fields, and when there are 50, 250, and 450 individuals in common across datasets. We use flat priors for all $m$ and $u$ parameters, run the Gibbs Sampler for 1000 iterations, and discard the first 100 as burn-in. Traceplots for parameters of interest for one example simulation are provided in Appendix \ref{app:appendix-sim}.

@@

Therefore we re-ran our analysis with fewer agreement levels for each field according to Table~\ref{Tab:el_salvador_cutoffs_2}, and
obtained analogous results. With 216 possible agreement patterns, 159
were realized in the data, and our proposed method, \texttt{fabl} became much faster,
finishing in 61 seconds. Meanwhile \texttt{BRL} took 239 seconds,
relatively unchanged from the first implementation. This demonstrates
the way that the computational complexity of our method depends on the
number of unique agreement patterns, and how significant computational
gains can be made by simplifying the construction of the comparison
vectors. The estimates of the \(\mathbf{m}\) parameters under each method are very similar, as shown in
Figure~\ref{fig:m-and-u}. Additionally, traceplots for parameters of interest are provided in Appendix \ref{app:appendix-es}

@@

\hypertarget{app:fabl-psuedocode}{%
	\subsection{Summary of Fast Beta Linkage Method}\label{app:fabl-psuedocode}}

\begin{algorithm}[h!]
	\begin{algorithmic}[1]

\hypertarget{appendix-sim}{%
	\subsection{Traceplots for Simulation Study}\label{app:appendix-sim}}

@@

\hypertarget{appendix-es}{%
	\subsection{Traceplots for El Salvador Case Study}\label{app:appendix-es}}
